\textls[-0]{\thetitle}

### 2022-11-11 stlc-compiled.tex
minor

[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLC}}@][@\tanc{c-STLC-subst-start}@]

@@

Def subst\_tm_unit :=

@@

Fact [@\textls[-20]{tm\_unit\_eq\_STLC}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.

@@

Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.

>>>>

[@\outdent@][@\codecomment{Code emitted for definition of \texttt{subst} in family \texttt{STLC}}@][@\tanc{c-STLC-subst-start}@]

@@

Def subst\_tm_unit :=[@\codecomment{\textls[-20]{emmited upon definition of case}}@]

@@

Fact [@\textls[-0]{tm\_unit\_eq\_STLC}@] : [@\dadada@]. reflexivity. Qed.

@@

Fact [@\textls[-0]{subst\_tm\_unit\_eq}@] : [@\dadada@]. reflexivity. Qed.
